### 2022-11-14 project_Antonio/paper.tex
Add files via upload

\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $\Upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory. For these studies the data of the LHC Run 2 (2015-2018) will be used corresponding to an integrated luminosity of about 150 fb$^{-1}$, this is 4 times larger than the dataset used for current results. Previously CMS has carried out studies with the data from 2017 ~\cite{2019134811} corresponding to 37.5 fb$^{-1}$ and ATLAS in 2015 ~\cite{Aad_2015} corresponding to 20.3 fb$^{-1}$.

>>>>

\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $\Upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory. For these studies the data of the LHC Run 2 (2015-2018) will be used corresponding to an integrated luminosity of about 150 fb$^{-1}$, this is 4 times larger than the dataset used for current results. Previously CMS has carried out studies with the data from 2017 ~\cite{2019134811} corresponding to 37.5 fb$^{-1}$ and ATLAS in 2015 ~\cite{PhysRevLett.114.121801} corresponding to 20.3 fb$^{-1}$.
